### 2013-04-18 article.tex
Generate diff of article changes
Signed-off-by: Michael Barton <mail@michaelbarton.me.uk>

  \item[Simple editing of a draft genome sequence.]{Genomer is built on the
  existing Scaffolder \cite{barton2012} file format for assembling draft genome
  sequences. This YAML \cite{yaml} format simplifies the process of
  re-organising and trimming contigs in draft genome without having to edit
  large nucleotide sequences manually.}

>>>>

  \item[Simple editing of a draft genome sequence.]{Genomer is built on the
  existing Scaffolder \cite{barton2012} file format for assembling draft genome
  sequences. This YAML format simplifies the process of re-organising and
  trimming contigs in draft genome without having to edit large nucleotide
  sequences manually.}
